Examining Whether Approximate Visualizations Impact Perception of Corrected Visualizations

### 2016-12-09 paper/paper.tex
fix a few open issues

@@

\begin{table}[!t]
% increase table row spacing, adjust to taste
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{The mean and standard deviation of the true and expected bias.}
\label{table_errors}
\centering
\begin{tabular}{|l||r|r|r|r|}
\hline
Question & Bias Type  & Mean  & Standard deviation \\ \hline
\hline
type 1   & true      &  0.010 & 0.195  \\ \hline
type 1   & expected  & -0.011 & 0.215  \\ \hline
type 2   & true      & -1.542 & 5.244  \\ \hline
type 2   & expected  & -0.145 & 0.691  \\ \hline
\end{tabular}
\end{table}

\todo{Daniel: mean and variance of measures and expected bias}

@@

The effect for question type 1 was smaller than the other question types (95\% CI -0.435-0.582).
This aligns with the finding that the error for this type of question was lower overall.
For question types 2 and 3, the sign of the impact of the expected bias was in the same direction of the bias ($95\% CI 2.594-5.637, 0.329-1.135$ for type 2 and 3, respectively).
This suggests that people tend to be biased in the same direction as the data they see in the approximate visualization.
However, for question type 2, the measured bias was \testit{larger} than the expected bias.

>>>>

Table \tabref{table_bias} summarizes participant responses.
For question type 1, both the true and expected biases are relatively small (e.g., about 10\% of the correct values).
For question type 2, the true biases averaged over 100\% of the correct values, with an even larger standard deviation.
This means that participant answers to question type 2 were off by orders of magnitude.

@@

\begin{table}[!t]
% increase table row spacing, adjust to taste
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{The mean and standard deviation of the true and expected bias.}
\label{table_bias}
\centering
\begin{tabular}{|l||r|r|r|r|}
\hline
Question & Bias Type  & Mean  & Standard deviation \\ \hline
\hline
type 1   & true      &  0.010 & 0.195  \\ \hline
type 1   & expected  & -0.011 & 0.215  \\ \hline
type 2   & true      & -1.542 & 5.244  \\ \hline
type 2   & expected  & -0.145 & 0.691  \\ \hline
\end{tabular}
\end{table}

@@

The effect for question type 1 was smaller than the other question types (95\% CI -0.435-0.582).
This aligns with the finding that the error for this type of question was lower overall.
For question types 2 and 3, the sign of the impact of the expected bias was in the same direction of the bias ($95\% CI 2.594-5.637, 0.329-1.135$ for type 2 and 3, respectively).
This suggests that people tend to be biased in the same direction as the data they see in the approximate visualization.
However, for question type 2, the measured bias was \textit{larger} than the expected bias.
